State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-12 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
paper edits - fixed typo in eq 14
paper edits - freq analysis section

@@

	&-& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 

@@

Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$. Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited. Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something. These kernel are kinda theoretical and I have not ever seen and estimate of the covariance function. Can we remove the sentence ``Such a condition is usually satisfied...'' }. Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$, where $\boldsymbol{\nu}_c$ is a cutoff frequency. Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$. Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy 
\begin{equation}
	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho_s\nu_{c}}, 
\end{equation}
where $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter. This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$. If the condition is not satisfied, spatial aliasing will occur.

@@

&-& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+

@@

&-&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 

>>>>

\omg{show figure with the Mexican hat here.}

@@

	&+& \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 

@@

Let the spectral representation of the dynamic field at time $t$ be denoted by $V_t(\boldsymbol{\nu})$.
Given $V_t(\boldsymbol{\nu})$, the distance between adjacent sensors should be no more than
% 
% Then, for an accurate representation, $V_t(\boldsymbol{\nu})$ needs to be spatially band-limited. Such a condition is usually satisfied due to the band-limiting effect of most practical kernels and covariance functions \todo{~cite\{some EEG literature here\}} \omg{will try to find something. These kernel are kinda theoretical and I have not ever seen and estimate of the covariance function. Can we remove the sentence ``Such a condition is usually satisfied...'' }. Thus we can assume that the spectral response $V_t(\boldsymbol{\nu})$ is band-limited with $V_t(\boldsymbol{\nu}) \approx 0 ~ \forall \boldsymbol{\nu} > \boldsymbol{\nu}_c$,  
% 
% Note that for the two-dimensional, homogeneous and isotropic fields being considered $\boldsymbol{\nu}_c = [\nu_c ~ \nu_c]^\top$. Given such a band-limited field the distance between adjacent sensors, $\Delta_s$, needs to satisfy 
\begin{equation}
	\label{eq:MinimumSensorDistance} \Delta_s < \frac{1}{2\rho_s\nu_{c}}, 
\end{equation}
where $\boldsymbol{\nu}_c$ the cut-off frequency, $\rho_s \in \mathbb{R} \ge 1$ is an oversampling parameter. This condition must be satisfied for the hidden dynamic field $v_t(\mathbf{r})$ to be precisely inferred from the sampled observations, $\mathbf{y}_t$. If the condition is not satisfied, spatial aliasing will occur.

@@

&+& \xi\int_\Omega {\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})d\mathbf{r}} \mathbf{x}_t+

@@

&+&\xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r})e_t(\mathbf{r})d\mathbf{r}}.\\ 
